---
title: "DATA VISULIZATION-SHINY"
author: "IAMIcey"
date: "2022-12-02"
output: html_document
runtime: shiny
---


## Funtion

```{r eruptions, echo=FALSE}
library(RSQLite)
library(stringr)
library(readr)
library(dplyr)
dcon <- dbConnect(SQLite(), dbname = '~/STAT605/final project/finalopen.db')

res <- dbSendQuery(conn = dcon, "
select `Issue.Date`, round(sum(`Amount.Due`),2) as l,
ifnull(sum(case when county = 'R' then  1 end),0) as r1,
ifnull(sum(case when county = 'BX' then  1 end),0) as r2,
ifnull(sum(case when county = 'Q' then  1 end),0) as r3,
ifnull(sum(case when county = 'NY' then  1 end),0) as r4,
ifnull(sum(case when county = 'K' then  1 end),0) as r5
from final_Open_Parking_and_Camera_Violations
where `Issue.Date` between '2018-01' and '2021-12'
group by `Issue.Date`;
")
df_flower <- dbFetch(res, -1)
dbClearResult(res)

df_flower_table <- df_flower
colnames(df_flower_table) <- c('Issue.Date','Amount.Due','R','BX','Q','NY','K')

for(i in 1:nrow(df_flower)){
  df_flower[i,3:7] <- order(as.matrix(df_flower[i,3:7]))/100
}
df_flower[,2] <- df_flower[,2]*(1.2)/(max(df_flower[,2])*2)
df_economy <- read.csv('~/STAT605/final project/Book1.csv')
df_economy$Date <- str_sub(as.Date(df_economy$Date,'%m/%d/%Y'),1,7)
df_economy <- df_economy %>% 
  filter(Date >= '2018-01' & Date <= '2021-12') %>% 
  group_by(Date) %>% 
  summarise(WEI = mean(WEI))
df_economy$WEI <- df_economy$WEI/20

library(ggplot2)
Eco_data <- as.data.frame(read_csv("~/STAT605/WEEK6/week 7/Book1.csv"))
Eco_data$Date <- as.Date(Eco_data$Date,'%m/%d/%Y')
Eco_from_2018 <- filter(Eco_data, Date >= '2018-01-01' )
Eco_from_2018['WEI 13 week moving average'] <- Eco_from_2018$WEI
for(i in 13:nrow(Eco_from_2018)){
  Eco_from_2018$`WEI 13 week moving average`[i] <- mean(Eco_from_2018$WEI[(i-12):i])
}
library(grid)
library(stringr)
library(scales)
library(DT)

x1 <- 0.7
y1 <- 0.3
### draw lines
draw_lines <- function(a,b,month = '01'){
  color_line <- get_color(month)
  grid.lines(x = c(x1,a),y = c(y1,b),gp=gpar(col = color_line ))
  grid.text(month,x = a,y = b,gp = gpar(fontsize=15))
}


### draw coordinate
draw_coor <- function(a,b,l){
  if(b == y1+0.1){
    if(a == x1){
      y <- y1 + l
      x <- x1
      coor <- c(x,y)
    }
    if(a != x1){
      l_ab <- sqrt((a-x1)^2+(b-y1)^2)
      y <- y1 + l * abs(b-y1)/l_ab
      x <- ((y - y1) * (a - x1)/(b - y1)) + x1
      coor <- c(x,y)
    }

  }
  if(b == y1-0.1){
    if(a == x1){
      y <- y1 - l
      x <- x1
      coor <- c(x,y)
    }
    if(a != x1){
      l_ab <- sqrt((a-x1)^2+(b-y1)^2)
      y <-y1 - l * abs(b-y1)/l_ab
      x <- ((y - y1) * (a - x1)/(b - y1)) + x1
      coor <- c(x,y)
    }

  }
  if(a == x1-0.1){
    l_ab <- sqrt((a-x1)^2+(b-y1)^2)
    x <- x1 - l * abs(a-x1)/l_ab
    y <- y1 + (b-y1)*(x-x1)/(a-x1)
    coor <- c(x,y)
    
  }
  if(a == x1+0.1){
    l_ab <- sqrt((a-x1)^2+(b-y1)^2)
    x <- x1 + l * abs(a-x1)/l_ab
    y <- y1 + (b-y1)*(x-x1)/(a-x1)
    coor <- c(x,y)
    
  }
  return(coor)
}

## draw the coordinate of date
date_coordinate <- function(date){
  
  seq_Date <- seq.Date(from = as.Date("2018-01-01",format = "%Y-%m-%d"), by = "month", length.out = 48)
  Date <- str_sub(as.character(seq_Date),1,7)
  x <- as.vector(0);x_top <- as.vector(0);x_right <- as.vector(0);x_bottom <- as.vector(0);x_left <- as.vector(0)
  y <- as.vector(0);y_top <- as.vector(0);y_right <- as.vector(0);y_bottom <- as.vector(0);y_left <- as.vector(0)
  for(j in 1:12){
    x_top[j] <- (x1-0.1)+0.2/13*j
    y_top[j] <- y1+0.1
  }
  for(j in 1:12){
    x_right[j] <- x1+0.1
    y_right[j] <- (y1+0.1)-0.2/13*j
  }
  for(j in 1:12){
    x_bottom[j] <- (x1+0.1)-0.2/13*j
    y_bottom[j] <- (y1-0.1)
  }  
  for(j in 1:12){
    x_left[j] <- (x1-0.1)
    y_left[j] <- (y1-0.1)+0.2/13*j
  }
  
  
  x <- c(x_top,x_right,x_bottom,x_left)
  y <- c(y_top,y_right,y_bottom,y_left)
  df_date <- data.frame(coordinate_x = x,coordinate_y = y, date = Date)
  
  locate <- as.vector(0)
  for(k in 1:length(date)){
    locate[k] <- which(str_detect(df_date$date,date[k]))
  }
  return(df_date[locate,1:2])
}
draw_circle <- function(a,b,r1,r2,r3,r4,r5,county,fill_p = 'grey'){
    if(sum(county == 'BX') == 1){
      x <- a + r1*cos(72*pi/180)
      y <- b + r1*sin(72*pi/180)
      grid.circle(x,y,r1,gp = gpar(col = 'red',lwd = 5,fill = fill_p,alpha = 0.5))
    }
    if(sum(county == 'K') == 1){
      x <- a - r2*cos(36*pi/180)
      y <- b + r2*sin(36*pi/180)
      grid.circle(x,y,r2,gp = gpar(col = 'blue',lwd = 5,fill = fill_p,alpha = 0.5))
    }
    if(sum(county == 'NY') == 1){
      x <- a - r3*cos(36*pi/180)
      y <- b - r3*sin(36*pi/180)
      grid.circle(x,y,r3,gp = gpar(col = 'orange',lwd = 5,fill = fill_p,alpha = 0.5))
    }
    if(sum(county == 'Q') == 1){
      x <- a + r4*cos(72*pi/180)
      y <- b - r4*sin(72*pi/180)
      grid.circle(x,y,r4,gp = gpar(col = 'green',lwd = 5,fill = fill_p,alpha = 0.5))
    }
    if(sum(county == 'R') == 1){
      x <- a + r5
      y <- b 
      grid.circle(x,y,r5,gp = gpar(col = 'pink',lwd = 5,fill = fill_p,alpha = 0.5))
    }
}

get_length <- function(date){
  as.vector(df_flower[which(df_flower$Issue.Date == date),][2:7])
}

draw_flower <- function(date,l = 0.3,r1 = 0.01,r2 = 0.02,r3 = 0.03,r4 = 0.04,r5 = 0.05,county = c('BX','NY','Q','K','R')){
  l <- get_length(date)$l
  r1 <- get_length(date)$r1
  r2 <- get_length(date)$r2
  r3 <- get_length(date)$r3
  r4 <- get_length(date)$r4
  r5 <- get_length(date)$r5
  a <- date_coordinate(date)[1,1]
  b <- date_coordinate(date)[1,2]
  c <- draw_coor(a,b,l)[1]
  d <- draw_coor(a,b,l)[2]
  m <- draw_economy(a,b,date,l)[1]
  n <- draw_economy(a,b,date,l)[2]
  draw_circle(c,d,r1,r2,r3,r4,r5,county)
  draw_lines(c,d,substring(date,6))
  return (c(m,n))
}

month <- c('01','02','03','04','05','06','07','08','09','10','11','12')
month_color <- data.frame(month =month, color = c(viridis_pal()(12)))
get_color <- function(month){
  month_color[which(month_color$month == month),2]
}

show_data <- function(date,county){
  index <- as.vector(0)
  for(i in 1:length(date)){
    index[i] <- which(df_flower_table$Issue.Date == date[i])
  }
  subset(df_flower_table[index,],select=c('Issue.Date','Amount.Due',county))
}

get_economy_li <- function(date){
  df_economy[which(df_economy$Date == date),2]
}

draw_economy <- function(a,b,date,l){
  l1 <- l + get_economy_li(date)$WEI
  draw_coor(a,b,l1)
}

```

## shiny plot


```{r,warning=FALSE,message=FALSE}
library(shiny)
library(shinyWidgets)
library(bubblyr)
library(shinyjqui)
library(echarts4r)
library(dplyr)
year <- c('2018','2019','2020','2021')
month <- c('01','02','03','04','05','06','07','08','09','10','11','12')
ui <- fluidPage(
  titlePanel("Violations in NY"),
  #bubbly(theme = "bigmom"),
      selectInput('effect', NULL, choices = get_jqui_effects()),
      actionButton('show', 'Show'),
      actionButton('hide', 'Hide'),
  sidebarLayout(
    sidebarPanel(
      pickerInput('Year', 'Choose a year', year,multiple = TRUE),
      pickerInput("choicePickermonth", "Choose month(s):", choices = month, multiple = TRUE),
      pickerInput("choicePickercounty", "Choose county(s):", choices = c(" Richmond(Pink)" = "R",
                     "Kings(Blue)" = "K",
                     "Queens(Green)" = "Q",
                     "Bronx(Red)" = "BX",
                     " New York(Yellow)" = "NY"), multiple = TRUE)),
    
    mainPanel(
            tabsetPanel(type = "tabs",
                  tabPanel("Plot", plotOutput("plot")),
                  #tabPanel("Summary", verbatimTextOutput("outyear"),
                           #verbatimTextOutput("outmonth"),
                           #verbatimTextOutput("outPicker")),
                  tabPanel("Table", DT::dataTableOutput("table")),
                  tabPanel("Economy Plot", echarts4rOutput("plot1"))),
              )
  ),
  switchInput('Economy of NY:',
   inputId = "Id014",
   onStatus = "success", 
    offStatus = "danger"
),#verbatimTextOutput("value")
)
server <- function(input, output) {
  library(grid)
  library(stringr)  
  output$outyear <- renderPrint({
    input$Year
  })
  output$outmonth <- renderPrint({
    input$choicePickermonth
  })

  output$outPicker <- renderPrint({
    input$choicePickercounty
  })
  observeEvent(input$show, {
    jqui_show('#plot', effect = input$effect)
  })
  
  observeEvent(input$hide, {
    jqui_hide('#plot', effect = input$effect)
  })
  #output$value <- renderPrint({input$Id014})
  output$plot <- renderPlot({
    if(length(input$choicePickermonth) >= 2){
    grid.newpage()
    vp <- viewport(x = 0.5, y = 0.5,width = 1,height = 1)
    pushViewport(vp)
    grid.rect(x1,y1,0.2,0.2)
    grid.text('2018',0.7,0.38)
    grid.text('2019',0.78,0.3,rot = -90)
    grid.text('2020',0.7,0.22)
    grid.text('2021',0.62,0.3,rot = 90)
      m_x <- as.vector(0)
      n_y <- as.vector(0)
      for(i in 1:length(input$Year)){
      for(t in 1:length(input$choicePickermonth)){
      time <- paste0(input$Year[i],'-',input$choicePickermonth[t])
      draw_flower(time,county = input$choicePickercounty)
      if(input$Id014 == 'TRUE'){
    grid.points(draw_flower(time,county = input$choicePickercounty)[1],draw_flower(time,county = input$choicePickercounty)[2])}
      m_x <- c(m_x,draw_flower(time,county = input$choicePickercounty)[1])
      n_y <- c(n_y,draw_flower(time,county = input$choicePickercounty)[2])
    }
      }
    if(input$Id014 == 'TRUE'){
    grid.xspline(m_x[-1],n_y[-1],gp = gpar(col = 'darkgreen'),shape = 0.3)} }
    
    if(length(input$choicePickermonth)<2) {
   grid.newpage()
    vp <- viewport(x = 0.5, y = 0.5,width = 1,height = 1)
    pushViewport(vp)
    grid.rect(x1,y1,0.2,0.2)
    grid.text('2018',0.7,0.38)
    grid.text('2019',0.78,0.3,rot = -90)
    grid.text('2020',0.7,0.22)
    grid.text('2021',0.62,0.3,rot = 90)
      m_x <- as.vector(0)
      n_y <- as.vector(0)
      for(i in 1:length(input$Year)){
      for(t in 1:length(input$choicePickermonth)){
      time <- paste0(input$Year[i],'-',input$choicePickermonth[t])
      draw_flower(time,county = input$choicePickercounty)
      if(input$Id014 == 'TRUE'){
    grid.points(draw_flower(time,county = input$choicePickercounty)[1],draw_flower(time,county = input$choicePickercounty)[2])}
      m_x <- c(m_x,draw_flower(time,county = input$choicePickercounty)[1])
      n_y <- c(n_y,draw_flower(time,county = input$choicePickercounty)[2])
    }
    }
    
    }},height = 400,width = 400)
  
  
  output$table <- DT::renderDataTable(DT::datatable({
    time <- as.vector(0)
    k <- 1
    for(i in 1:length(input$Year)){
      for(j in 1:length(input$choicePickermonth)){
        time[k] <- paste0(input$Year[i],'-',input$choicePickermonth[j])
        k <- k+1
      }
    }
    show_data(time,input$choicePickercounty)
  }))
  
  output$plot1 <- renderEcharts4r({
    
Eco_plot <- Eco_from_2018 %>%
  e_charts(x = Date) %>%
  e_line(serie = WEI) %>%
  e_line(serie = `WEI 13 week moving average`) %>%
  e_tooltip(trigger = "axis",axisPointer = list(type = "cross")) %>%
  e_datazoom(type = "slider")
Eco_plot %>%
  e_grid(right = '15%') %>%
  e_legend(orient = 'vertical', 
           right = '5', top = '15%') %>%
  e_title(text = 'Weekly Economic Index (WEI) of NewYork City',left = "center")
  

  })
}

shinyApp(ui,server)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



